---
title: "Advanced Regression Techniques: Ames, Iowa Housing Data"
output: html_notebook
---

## Prerequisites

```{r}
library(tidyverse)
library(caret)
library(e1071)
library(doMC)
library(Metrics)
```

## Load data

```{r}
ames_train <- read_csv("data/train.csv")
ames_test <- read_csv("data/test.csv")
```

## Preprocessing

```{r}
glimpse(ames_train)
```

```{r}
glimpse(ames_test)
```

## Combine train and test for common preprocessing

Remove `SalePrice` column
```{r}
sale_price_train <- ames_train %>% 
  select(SalePrice)
ames_train <- ames_train %>% 
  select(-SalePrice)
```

Concatenate `train` and `test` rows

```{r}
all <- bind_rows(ames_train, ames_test)
dim(all)
```

Convert `factor` to `chr` for preprocessing

```{r}
all <- all %>% 
  mutate_if(is.factor, as.character)
```


Count number of missing values

```{r}
plot_n_missing <- function(df) {
  df %>% 
    gather(key = "predictors", value = "values") %>% 
    mutate(is_missing = is.na(values)) %>% 
    filter(is_missing == TRUE) %>% 
    group_by(predictors) %>% 
    summarise(n_missing = sum(is_missing)) %>%
    arrange(desc(n_missing)) %>% 
    ggplot(aes(reorder(predictors, n_missing), n_missing)) +
      geom_bar(stat = "identity") +
      coord_flip() +
      labs(x = "Predictors", 
           y = "number of missing values")
}
plot_n_missing(all)
```

Lets fill some missing values 

```{r}
all <- all %>%
  replace_na(list(
    PoolQC = "None", # does not own pool
    MiscFeature = "None", # no extra features worth mentioning
    Alley = "None", # does not have alley
    Fence = "None", # does not have fence
    FireplaceQu = "None",# does not have fireplace
    LotFrontage = 0, # is not connected to street
    GarageType = "None", # does not have garage
    GarageYrBlt = 1000, # does not have garage, assign atypical year
    GarageQual = "None", # does not have garage
    GarageFinish = "None", # does not have garage
    GarageCond = "None", # does not have garage
    GarageCars = 0, # does not have garage
    GarageArea = 0, # does not have garage
    BsmtFinType2 = "None", # does not have basement
    BsmtExposure = "None", # does not have basement
    BsmtQual = "None", # does not have basement
    BsmtFinType1 = "None", # does not have basement
    BsmtCond = "None", # does not have basement
    BsmtHalfBath = 0, # does not have basement
    BsmtFullBath = 0, # does not have basement
    BsmtFinSF1 = 0, # does not have basement
    BsmtFinSF2 = 0, # does not have basement
    TotalBsmtSF = 0, # does not have basement
    MasVnrType = "None", # does not have masonry
    MasVnrArea = 0 # does not have masonry
    )) 

plot_n_missing(all)
```

*NB*:Rest of the missing values will be imputed using `knn`

Convert `chr` to `factor` for use in algorithms

```{r}
all <- all %>% 
  mutate_if(is_character, as.factor) %>% 
  mutate(MSSubClass = as.factor(MSSubClass)) # change from int to fctr
```

Seperate `train` and `test`
```{r}
ames_train <- all %>% 
  filter(Id <= 1460)
ames_test <- all %>%
  filter(Id > 1460)
```


Get rid of `id` column
```{r}
# train Id
ames_train_id <- ames_train %>% 
  select(Id)
ames_train <- ames_train %>%
  select(- Id)
# test Id
ames_test_id <- ames_test %>% 
  select(Id)
ames_test <- ames_test %>% 
  select(- Id)
```


Apply transformation on Saleprice and convert X to `data.frame` for `caret`

```{r}
ames_train <- ames_train %>% as.data.frame()

sale_price_train <- sale_price_train %>% select(SalePrice) %>% log()

ggplot(sale_price_train, aes(SalePrice)) +
  geom_freqpoly() +
  geom_rug(alpha = 3/4)
```



## Modelling

### GBM

```{r}
#registerDoMC(cores = 2)

fitControl <- trainControl(## 10-fold CV
                           method = "repeatedcv",
                           number = 10,
                           ## repeated five times
                           repeats = 5)

gbmGrid <-  expand.grid(interaction.depth = 3,
                        n.trees = c(10, 200, 700, 1000), 
                        shrinkage = 0.01,
                        n.minobsinnode = 10
                        )
                        
nrow(gbmGrid)

set.seed(77)
system.time(
gbmFit <- train(x = ames_train, 
                y = sale_price_train$SalePrice,
                method = "gbm", 
                preProcess = c("knnImpute"),
                trControl = fitControl,
                verbose = FALSE, 
                 ## Now specify the exact models 
                 ## to evaluate:
                tuneGrid = gbmGrid)
)
gbmFit
```

```{r}
ggplot(gbmFit)
```

### XGB


```{r}

maeSummary <- function (data,
                        lev = NULL,
                        model = NULL) {
   out <- mae(data$obs, data$pred)  
   names(out) <- "MAE"
   out
}

fitControl <- trainControl(## 10-fold CV
                           method = "repeatedcv",
                           number = 10,
                           ## repeated five times
                           repeats = 5,
                           ## mean absolte error
                           summaryFunction = maeSummary)

xgbGrid <-  expand.grid(nrounds = c(700, 1000, 1300, 1500, 1700, 2000),
                        max_depth = 5,
                        eta = 0.01,
                        gamma = 0,
                        colsample_bytree = 0.6,
                        min_child_weight = 1,
                        subsample = 0.6
                        )
                        
nrow(xgbGrid)

set.seed(77)
system.time(
xgbFit <- train(x = data.matrix(ames_train), 
                y = sale_price_train$SalePrice,
                method = "xgbTree", 
                preProcess = c("knnImpute"),
                trControl = fitControl,
                metric = "MAE",
                maximize = FALSE,
                 ## Now specify the exact models 
                 ## to evaluate:
                tuneGrid = xgbGrid)
)
xgbFit
```


```{r}
xgbFit$results %>% 
  ggplot(aes(nrounds, MAE)) +
    geom_line() +
    geom_point() +
    geom_errorbar(aes(ymin = MAE - MAESD, ymax = MAE + MAESD))
```

```{r}
ggplot(xgbFit)
```

```{r}
xgbFit$resample
```


Make prediction

```{r}
ames_test_sale_price <- predict(xgbFit, ames_test)
```

Save results
```{r}
str(exp(ames_test_sale_price))
```


```{r}
submission <- tibble(Id = ames_test_id$Id,
                     SalePrice = exp(ames_test_sale_price))
submission %>% write_csv("data/submission.csv")
```

